2H qSIP Calculations

### 2022-03-15 qSIP_calculations.Rmd
Loade F_L 2F data

@@

```{r}
# Combine triplicate samples into one
FID_results_trip <- FID_results %>% 
  # Remove standards and fractions
  filter(sample_id != "FAME37.1") %>% 
  filter(sample_id != "TCBAME-2") %>% 
  filter(!str_detect(sample_id, "F1")) %>% 
  filter(!str_detect(sample_id, "F2")) %>% 
  filter(!str_detect(sample_id, "F3")) %>% 
  filter(!str_detect(sample_id, "cr")) %>%
  mutate(sample_rep = str_remove(sample_id, "[xyz]")) %>% 
  group_by(sample_rep, compound) %>%
  # Generate summary stats
  summarize(
    rel_area_FID_max = max(rel_area_FID, na.rm=TRUE),
    rel_area_FID_min = min(rel_area_FID, na.rm=TRUE),
    rel_height_FID_max = max(rel_height_FID, na.rm=TRUE),
    rel_height_FID_min = min(rel_height_FID, na.rm=TRUE),
    rt_FID = mean(rt_FID, na.rm=TRUE),
    rel_area_FID = mean(rel_area_FID, na.rm=TRUE),
    rel_height_FID = mean(rel_height_FID, na.rm=TRUE)) %>% 
  # Add some basic metadata
  mutate(
  inc_time = case_when(
    str_detect(sample_rep, "...0") ~ 0,
    str_detect(sample_rep, "...3") ~ 3,
    str_detect(sample_rep, "...7") ~ 7),
  site = case_when(
    str_detect(sample_rep, "c") ~ "Conifer",
    str_detect(sample_rep, "t") ~ "Tundra",
    str_detect(sample_rep, "g") ~ "Grassland",
    str_detect(sample_rep, "m") ~ "Meadow")
  )
```

## Remove standards from gencalcs
```{r}
# Don't want our standard compounds to be used for generation time calculations! x_x
peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros_FID %>% 
  filter(str_detect(compound, "STD", negate = TRUE))
```

>>>>

## Load F_L 2F Data

```{r}
F_L_2F <- read_csv("data/Label_2H_Data/dD_cleaned.csv") %>% 
  group_by(soil) %>% 
  summarize(F_label_ppm_mn = mean(F_label_ppm),
            F_label_ppm_se = sd(F_label_ppm)) %>% 
  mutate(terrain = case_when(
    soil == "Conifer" ~ "Gordon Gulch Conifer Forest",
    soil == "Tundra" ~ "Niwot Ridge Tundra",
    soil == "Grassland" ~ "Marshall Mesa Grassland"
  ))
```

@@

## Correct for PAME

```{r}
## PICK UP HERE

peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros_FID %>% 
  # Don't want our standard compounds to be used for generation time calculations! x_x
  filter(str_detect(compound, "STD", negate = TRUE)) %>% 
  # Determine number of carbons in alkyl chain
  mutate(n_C = NA)
